Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-01 ms.qmd
Fixed table because theer was some very weird stuff going on with brms model...

   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)
      summary(model3.2_bayes)                            
  # Save model1.2
  saveRDS(model3.2, file = "./output/models/lnVRQ10_3.2")
  saveRDS(model3.2_bayes, file = "./output/models/lnVRQ10_3.2_bayes")

@@

 # Extract the fixed / population-level effect summaries of the posterior
    fixed <- summary(model3.2_bayes)$fixed[,1:4]
    fixed <- cbind(Parameter = rownames(fixed), fixed)
    rownames(fixed) <- NULL

 # Extract the random effect summaries of the posteriors (SDs)
    random <- plyr::ldply(summary(model3.2_bayes)$random)[,1:5]
    colnames(random)[1] <- "Parameter"

# Create the table
    tabs1 <- rbind(fixed, random)
   tabs1$Parameter <- c("Intercept", "Acclimation Time (z scaled)", "Acclimation Effect", "Habitat (Marine)", "Habitat (Terrestrial)", "Acclimation*Marine", "Acclimation*Terrestrial", "Study", "Phylogeny", "Species", "Trait")

    flextable(tabs1) %>% flextable::bold(part = "header") %>% flextable::autofit() %>% flextable::add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% flextable::compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
```

>>>>

   model3.2_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 | spp) + (1|trait), data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnVRQ10_data)

  # Save model1.2
  saveRDS(model3.2, file = "./output/models/lnVRQ10_3.2")
  saveRDS(model3.2_bayes, file = "./output/models/lnVRQ10_3.2_bayes")

@@

 # Extract the fixed / population-level effect summaries of the posterior
    fixed <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^b"), 2,  function(x) post_summary(x)))
    fixed <- cbind(Parameter = c("Intercept", "Acclimation Time (z scaled)", "Acclimation Effect", "Habitat (Marine)", "Habitat (Terrestrial)", "Acclimation*Marine", "Acclimation*Terrestrial"), fixed)
    rownames(fixed) <- NULL

 # Extract the random effect summaries of the posteriors (SDs)
    random <- do.call(rbind, apply(posterior_samples(model3.2_bayes, pars = "^sd"), 2,  function(x) post_summary(x)))
    random <- cbind(Parameter = c( "Study", "Phylogeny", "Species", "Trait"), random)
    rownames(random) <- NULL

# Create the table
    tabs1 <- rbind(fixed, random)

    flextable(tabs1) %>% bold(part = "header") %>% autofit() %>% add_body_row(values = as_paragraph(as_b("Fixed Effects")), top = TRUE, colwidths = 5) %>% compose(value = as_paragraph(as_b(c(("Random Effects"), rep("", 4)))), i = 8)
```
